Effect of Heteroscedasticity in Covariance Matrix

### 2014-12-22 thesis/draft4.tex
Work on the paper with Sven.

>>>>

QQ-plots of the smallest/largest eigenvalues are shown in
figure \ref{fig:eigmin_qq_plot} and \ref{fig:eigmax_qq_plot}. It is
clearly seen that normal distributions are fairly good approximation
to the distribution of the smallest eigenvalue in all cases, and the
largest eigenvalue in all but the last two values of $v$, namely $v =
0.05$ and $v = 0.08$.
\begin{figure}[htb!]
  \centering
  \includegraphics[scale=0.6]{../pics/eigmin_dist.eps}
  \caption{\small \it QQ-plot of the smallest eigenvalues}
  \label{fig:eigmin_qq_plot}
\end{figure}

\begin{figure}[htb!]
  \centering
  \includegraphics[scale=0.6]{../pics/eigmax_dist.eps}
  \caption{\small \it QQ-plot of the largest eigenvalues}
  \label{fig:eigmax_qq_plot}
\end{figure}
